### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 65536& 16.0& 1&0&0.04&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
One-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&0 &&& 1.1 MB &  \\
AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &&& 1.1 MB &  \\
AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &0&&& 1.0 MB   \\
AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &0&&& 909 KB\\
AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0&0&  &&1.1 MB \\
AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0& &&4.4 MB\\
RC4 mbedTLS 2.15& 65536 & 16.0 &2 &2 & & & & 1.1 MB\\
RC4 OpenSSL 1.1.0& 65536 & 16.0&2 &2 & & & & 1.0 MB\\
RC4 OpenSSL 1.1.1& 65536 & 16.0&2 &2 & & & & 896 KB\\
RC4 wolfSSL 4.5.0& 65536 & 16.0&2 &2 & & & &886 KB\\
RSA mbedTLS 2.15& 4096 & 12.0 &&&& &&1.8 MB\\
RSA OpenSSL 1.1.0& 4096 & 12.0 &&&& && 11 MB\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &&&& &&13 MB\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &&&& &&4.2 MB\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &&&& &&4.4 MB\\
Tiny DNN & 12000 & 13.6 & &&&&& 4.4 MB \\
GDK 3.24.23 & 65535 & 16.0 & &&&&& 48 MB\\
\bottomrule
\end{tabular}
}

@@

\subsubsection{Lookup Table}
\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
static const uint8_t T[16] = {
      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U};
...
output = (T[(key[i]>>24)] << 24) ^
         (T[(key[i+1]>>16) & 0xff] << 16) ^
         (T[(key[i+2]>>8) & 0xff] << 8) ^
         (T[(key[i+3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Small Entries.}\label{fig:chapter5:small_lookup}
\end{figure}

\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
static const uint32_t T[16] = {
    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
...
output = (T[(key[i+0]>>24)] << 24) ^
         (T[(key[i+1]>>16) & 0xff] << 16) ^
         (T[(key[i+2]>>8) & 0xff] << 8) ^
         (T[(key[i+3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Big Entries.}\label{fig:chapter5:big_lookup}
\end{figure}

>>>>

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 65536& 16.0& 1&0&0.04&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
One-byte Lookup Table & 65536 & 16.0& 1&1&9.8& 3.6 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 65536 & 16.0& 1&1&9.6& 8.5 & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&11.6 &6.7& -& 1.1 MB &65 min & 0.8 min & 0.1 min  \\
AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &0&-& 1.1 MB & 45 min & 0 min & 0 min  \\
AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &0.11 & 0&-& 1.0 MB  & 49 min & 0.2 min & 0 min \\
AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &0&&& 909 KB\\
AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0&0&  &&1.1 MB \\
AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0& &&4.4 MB\\
RC4 mbedTLS 2.15& 65536 & 16.0 &2 &2 & & & & 1.1 MB\\
RC4 OpenSSL 1.1.0& 65536 & 16.0&2 &2 & & & & 1.0 MB\\
RC4 OpenSSL 1.1.1& 65536 & 16.0&2 &2 & & & & 896 KB\\
RC4 wolfSSL 4.5.0& 65536 & 16.0&2 &2 & & & &886 KB\\
RSA mbedTLS 2.15& 4096 & 12.0 &&&& &&1.8 MB\\
RSA OpenSSL 1.1.0& 4096 & 12.0 &&&& && 11 MB\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &&&& &&13 MB\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &&&& &&4.2 MB\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &&&& &&4.4 MB\\
Tiny DNN & 12000 & 13.6 & &&&&& 4.4 MB \\
GDK 3.24.23 & 65535 & 16.0 & &&&&& 48 MB\\
\bottomrule
\end{tabular}
}

@@

\subsubsection{Lookup Table}
\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
static const uint8_t T[1024] = {
      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U,
...
output = (T[(key[i]>>24)] << 24) ^
         (T[(key[i+1]>>16) & 0xff] << 16) ^
         (T[(key[i+2]>>8) & 0xff] << 8) ^
         (T[(key[i+3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Small Entries.}\label{fig:chapter5:small_lookup}
\end{figure}

\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
static const uint32_t T[256] = {
    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
...
output = (T[(key[i+0]>>24)] << 24) ^
         (T[(key[i+1]>>16) & 0xff] << 16) ^
         (T[(key[i+2]>>8) & 0xff] << 8) ^
         (T[(key[i+3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Big Entries.}\label{fig:chapter5:big_lookup}
\end{figure}
